Mixture-of-tastes models for representing users with diverse interests

### 2017-11-12 paper/paper.tex
Add conclusion.

\section{Conclusion}

>>>>

\section{Conclusion}
We show that mixture-of-tastes representations are clear improvements over their baseline modes, especially in sequence-based settings where the accuracy gains come at a very modest cost in model complexity. We have taken care to test the mixture models against strong baselines, and have confidence that our approach can translate to accuracy gains in production recommender systems.
